Trends of SDR in Thessaloniki 

### 2022-10-13 Article.Rmd
Commit 2022-10-13 14:17

output:
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         no
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
  html_document:
    toc:        true
    fig_width:  7.5
    fig_height: 5
date: "`r format(Sys.time(), '%F')`"

@@

<!-- measurement -->
For both CM21 and CHP1 instruments, the mean signal and the standard deviation over one minute is recorded every one minute.
<!-- screening -->
A manual screening processes, removes inconsistencies and erroneous recordings, that can occur on a long contentious operation, like this one.
<!-- physical quantities -->
The conversion to irradiance was done using the available calibrations factors. For CHP1, there is only the initial one by the manufacture, and for CM21 there are seven calibration procedure in the span of the period we investigate.
<!-- Dark signal -->
We have adjusted the measurements for the dark signal offset, by a daily value, using the nights before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied, adjusted for the site, based on methods of Long and Shi\ [-@long_automated_2008; -@Long2006]. Only data characterized as good quality were used in this stud.
<!-- Data preparation -->
Due to larger measurement uncertainty near the horizon, we exclude
all measurements with SZA greater than $85^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we remove data with Azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$. At 
those cases the Sun, were not visible by the instruments.

@@

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all values to the mean Sun and Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the the Suns intensity variability, using an homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->

>>>>

output:
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
  html_document:
    toc:        true
    fig_width:  7.5
    fig_height: 5
date: "`r format(Sys.time(), '%F')`"

@@

<!-- measurement -->
For both CM21 and CHP1 instruments, the mean signal and the standard deviation over one minute is recorded every one minute.
<!-- screening -->
A manual screening processes, removes inconsistencies and erroneous recordings, that can occur on a long contentious operation, like this one.
<!-- physical quantities -->
The conversion to irradiance was done using the available calibrations factors. For CHP1, there is only the initial one by the manufacture, and for CM21 there are seven calibration procedure in the span of the period we investigate.
<!-- Dark signal -->
We have adjusted the measurements for the dark signal offset, by a daily value, using the nights before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied, adjusted for the site, based on methods of Long and Shi\ [-@long_automated_2008; -@Long2006]. Only data characterized as good quality were used in this study.
<!-- Data selection -->
Due to larger measurement uncertainty near the horizon, we exclude
all measurements with SZA greater than $`r 90-MIN_ELEVA`^\circ$. 
Moreover, due to some obstructions around the site (hills and buildings), we remove data with Azimuth angle between 
$35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$. At 
those cases the Sun, were not visible by the instruments.

@@

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all 1-minute values to the mean Sun and Earth distance.
<!-- TSI -->
<!-- And, we made all measurements relative to the TSI at 1au, in order to compensate for the the Suns intensity variability, using an homogenized timeseries of satellite TSI observations. As a result, we processed all radiation data as a fraction of Suns TSI. -->
